### 2020-05-29 Report/aws_325ghz_study.tex
new updates in Sec6 and 8

We will simply treat cases that matches a correction below a certain value as
``clear-sky''. If the correction limit is denoted as $dtb_{cs}$, the threshold
value, $x_{cs}$, is obtained by inverting the polynomial fit:
\begin{equation}
x_{cs} = f_{cs}^{-1}(dtb_{cs}) 
\label{eq:dtb}
\end{equation}
That is, if $x_m>x_{cs}$ a measurement is classified as clear-sky. If
$x_m\leq x_{cs}$, the measurement is rejected if a pure filtering is made, or
it is adjusted if the correction scheme is applied. We will largely set
$dtb_{cs}$ based on the noise level of the 183\,GHz channel involved, to be
1$\sigma$ or 2$\sigma$ where $\sigma$ refers to the magnitude of measurement
noise (Eq.~\ref{eq:noise}, often called NE$\Delta$T).

\subsection{Application of correction scheme}
%
In this section, we test the applicability of the correction scheme in detail.
To analyse the performance of the approach, we apply it to correct the
measurements from C1 using data from C2. Without the availability of actual
data, the simulation dataset but with noise added is used mimic the measurements. The
noise for individual channels is calculated according to
Equation~\ref{eq:noise}. As an example, the results from the channel
combination AWS-34 and AWS-42 are shown.

To test the efficacy of the correction scheme, three different models: linear,
quadratic and cubic are evaluated to fit the TB differences between C1 and C2.
For all three models, cases with $Tb2-Tb1 < $ -15\,K are assumed to be ``too
cloudy'' and are not corrected. The clear-sky adjustment for all eligible
measurements (without clear/cloudy classification) is calculated from all three
models, and the three predicted datasets are compared. The error in the
predicted measurements is assessed as the deviation to corresponding noise-free
clear-sky value.

The occurrence frequency of the deviations from three models is shown in
Fig.~\ref{fig:correction:c34-42:fit}. The occurrence frequency of the
measurements without any filtering or correction is also plotted as reference
(orange colour). If all measurements are devoid of any cloud impact, the
deviations should follow the Gaussian distribution of noise. However, in real
scenarios, the distribution is skewed due to the impact of clouds. Among the
three models, the quadratic and cubic models work better than the linear model.
Both quadratic and cubic models are able to correct the cloud impact in the
measurements, however the values of average bias indicates that the cubic model
performs better. The average deviation in the dataset is -0.75\,K and after
correction with a cubic model, it reduces to -0.05\,K, while for quadratic
model, the average bias after correction is 0.22\,K. For all other results
described further, a cubic model is used. It should also be noted that since no
clear/cloudy classification is included, the peak of the distributions
(representing the clear-sky cases) is reduced in the corrected datasets. To
avoid correcting the clear cases, implementation of clear/cloudy classification
is extremely important. [* I still don't get the last part. Do you mean that you
apply the correction on all data? *]

To implement the clear/cloudy classification as discussed in the previous
section, two different values of $dtb_{cs}$ are tested: $1\sigma$ and
$2\sigma$. For both values of $dtb_{cs}$ the corresponding clear-sky cut-off
($x_{cs}$) is calculated using Eq~\ref{eq:dtb}.
Figure~\ref{fig:correction:c34-42} shows the deviation of the uncorrected and
corrected measurements to their noise-free clear-sky values. The results from
\cite{rekha2012potential} are also shown as reference (see Sec.~\ref{sec:rekha}
for our assumptions). In order to allow a more direct comparison of our
approach with \cite{rekha2012potential}, we also include the
dataset,``Filtered'', where all cloudy cases are rejected. Apart from the fit
based cloudy classification, it is also assumed that cases with $Tb2-Tb1 < $
-15\,K are ``too-cloudy'', and are rejected. Various metrics corresponding to
the Figure~\ref{fig:correction:c34-42} are shown in
Table~\ref{tab:correction:stats:34:42}. [* Why are the yellow lines so
different in Figs.~10 and 11? Maybe we discussed it, but I have then forgot. *]

\begin{figure}[!p]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_AWS-34_AWS-42_allfits}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction, corrected using a linear,
      quadratic and cubic model. The distribution of noise alone is also shown
      as reference. The measurements have been corrected using brightness
      temperatures from AWS-42. The mean value of each distribution is given in
      parenthesis in the legend. Cases with $Tb2 - Tb1 > -15$\,K are rejected.}
	\label{fig:correction:c34-42:fit}
\end{figure}
%
\begin{figure}[!p]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_AWS-34_AWS-42_all}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction. The measurements have been
      corrected using a cubic model. The different datasets are: noise
      (simulation dataset), uncorrected-all (measurement dataset without
      clear/cloudy classification), filtered $1\sigma$ (cloudy measurements are
      filtered with $dtb_{cs}$ = 1$\sigma$), corrected $1\sigma$ (cloudy
      measurements are corrected with $dtb_{cs}$ = 1$\sigma$), corrected
      $2\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ =
      2$\sigma$), Sreerekha (measurements are filtered according to criteria
      described in \citet{rekha2012potential}).}
	\label{fig:correction:c34-42}
\end{figure}
%

\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness  & fraction  \\
							&   [K]  &   [K] & [K] & rejected [\%]\\
		\hline
		noise             		&   0.00 &  0.63 &               0.00 &                - \\
		uncorrected-all       	&  -0.19 &  0.87 &              -2.42 &                - \\
		filtered($1\sigma$ ) 	&  -0.10 &  0.66 &              -0.15 &               10.56 \\
		corrected($1\sigma$) 	&  -0.05 &  0.72 &              -0.23 &                2.84 \\
		corrected($2\sigma$) 	&  -0.09 &  0.70 &              -0.49 &                2.84 \\
		sreerekha et al   		&  -0.14 &  0.73 &              -0.76 &               43.60 \\
		\hline
	\end{tabular}
	\caption{Bias, standard deviation (std), and measure of skewness of
      deviations of the measurements to noise-free clear-sky cases. The
      fraction rejected describes the percentage of cases which are removed.
      The different datasets are: noise (simulation dataset), uncorrected-all
      (measurement dataset without clear/cloudy classification), filtered
      $1\sigma$ (cloudy measurements are filtered with $dtb_{cs}$ = 1$\sigma$),
      corrected $1\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ =
      1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with
      $dtb_{cs}$ = 2$\sigma$), Sreerekha (measurements are filtered according
      to criteria described in \cite{rekha2012potential}). }
	\label{tab:correction:stats:34:42}
\end{table}
%
\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness  & fraction  \\
		&   [K]  &   [K] & [K] & rejected [\%]\\
		\hline
	noise             		&   0.00 &  0.63 &              -0.01 &                - \\
	uncorrected       		&  -0.29 &  1.00 &              -2.62 &                - \\
	filtered($1\sigma$)  	&  -0.13 &  0.68 &              -0.25 &               17.54 \\
	corrected($1\sigma$) 	&  -0.06 &  0.76 &              -0.46 &                4.99 \\
	corrected($2\sigma$) 	&  -0.11 &  0.75 &              -0.69 &                4.99 \\
	sreerekha et al   		&  -0.20 &  0.78 &              -1.00 &               45.36 \\	
		\hline
\end{tabular}
\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for thinned dataset. 50\% of the clear cases are removed to improve the representation of cloudy cases }
\label{tab:correction:stats:34:42:thinned}
\end{table}

The distributions of filtered data are non-Gaussian. The right side of the
distribution follows measurement noise while the left side is skewed. The
skewness in the distribution is due to cloud impacts which pass through the
clear-sky threshold. The higher skewness in ``Sreerekha et al'' is mainly
caused by that their method only aims at removing cloud impacts above 4\,K.
Their approach also leads to a high rejection fraction (43.6\%). The filtering
method introduced here leads to a considerable lower rejection of data
(10.6\%).

[* The unit for skewness is said to K. Is that correct? In any case I suggest
to add an equation/description of skewness *]

If the correction part is added, the rejection is decreased even further (28\%)
and the bias is also improved (from -0.10 to -0.05\,K). On the other hand, the
correction gives some increase in standard deviation and skewness, compared to
filtering alone. A correction using $2\sigma$ as threshold between clear/cloudy
gives poorer performance, in particular the skewness is increased.

In Sec.~\ref{sec:validation} the validation of simulations against ATMS data
(Fig.\ref{fig:pdf:c16-22}) showed that the cloudy cases in the simulations were
underrepresented in comparison to the observations. In order to have a higher
representation of cloudy cases, we thinned the measurement dataset by removing
50\% of the clear-sky cases. The results from this smaller dataset, before and
after filtering/correction are shown in
Table~\ref{tab:correction:stats:34:42:thinned}. In comparison to the original
dataset, the statistics in the thinned dataset is slightly worse, as expected.
But overall the performance of the correction scheme is comparable. For all
further analysis presented in this report, the thinned dataset is used.
%
\subsection{Application of correction scheme using AWS-4X}
%
\begin{figure}[!t]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_AWS-32_AWS-4X_thinned}
	\caption{Same as Fig.~\ref{fig:correction:c34-42}, but for channel combinations AWS-32 and AWS-4X.}
	\label{fig:correction:c32-4X:thinned}
\end{figure}
%

@@

Fig.~\ref{fig:correction:c32-4X:thinned} shows the deviations of the
measurements to clear-sky values before and after correction, and the
corresponding metrics are provided in Table~\ref{tab:correction:stats:32:4X}.
With clear/cloudy classification for $dtb_{cs} = 1\sigma$, around 85\% of the
total measurements are classified as cloudy and are rejected in pure-filtering.
Rejecting all the cloudy cases reduces the average bias in the measurements
from -0.62\,K to -0.21\,K, while with the approach from
\citet{rekha2012potential} only 45\% of the data is rejected and the average
bias reduces to -0.41\,K. When all the cloudy cases, except the ``too cloudy'',
are corrected, the total bias increases to 0.88\,K. The unusually high fraction
of cloudy cases and an increase in bias on correction suggests misclassification
of clear cases as cloudy. Since, the weighting functions of AWS-32 and AWS-4X
are poorly matched, their relationship is inadequate to estimate the cloud
impact in AWS-32. Without any additional information, the regression approach
can only provide a successful filtering in comparison to the original approach
described by \citet{rekha2012potential}, although at the cost of high rejection
fraction. Additional information e.g., TB from other channels, is necessary
improve the accuracy of the correction.

\begin{table}[!h]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std & skewness & fraction \\
						&   [K]  &   [K] & [K] 		& rejected [\%]\\
		\hline
Noise             		&  -0.00 &  0.45 &               0.01 &                - \\
uncorrected       		&  -0.62 &  1.77 &              -4.61 &                - \\
filtered($1\sigma$)  	&  -0.21 &  0.51 &              -0.65 &               85.43 \\
corrected($1\sigma$) 	&   0.88 &  1.76 &              -1.30 &                5.35 \\
corrected($2\sigma$) 	&   0.76 &  1.80 &              -1.07 &                5.35 \\
sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               45.36 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combinations: AWS-32 and AWS-4X.   }
	\label{tab:correction:stats:32:4X}
\end{table}

@@

[* The values for uncorrected differ between Table 6 and 7? Can't be correct. *]

Table~\ref{tab:correction:stats:32:41} shows the statistics when AWS-32 is
corrected using AWS-41. The statistics of the filtered dataset are better than
the approach by \cite{rekha2012potential}, while the corrected data have poorer
statistics. This is not surprising as the weighting function match between
AWS-32 and AWS-41 is poor. The correction using $2\sigma$ as threshold works
better $1\sigma$. This is an exception, the reversed is valid for AWS-34/42 (as
mentioned) and the channel combinations discussed below.

Table~\ref{tab:correction:stats:33:41} shows the statistics when AWS-33 is
corrected using AWS-41. The TB differences for this combination and the cloud
impact in AWS-33 are highly correlated. Rejecting the cloudy cases reduces the
average bias in the measurements from -0.33\,K to -0.13\,K, while a correction
of cloudy cases reduces the bias further to 0.05\,K. A similar performance is
seen for the combination AWS-35 and AWS-43, and
Table~\ref{tab:correction:stats:35:43} shows the statistics from this
combination. After correction the bias due to cloudy measurements reduces
-0.33\,K to -0.05\,K while rejecting only 6.88\% of the total cases.

Table~\ref{tab:correction:stats:36:43} shows the statistics when AWS-36 is
corrected using AWS-43. For this combination, the weighting functions have a
poor match, but the TB differences and the cloud impact are strongly
correlated, as the cloud impact in AWS-36 is relatively low in comparison to
other 183\,GHz channels. The low fraction of rejection (7.38\%) also shows that
most of the measurements are without cloud impact. However, the small fraction
of cloudy cases which are corrected helps in successfully reducing the average
bias from -0.16\,K to 0.07\,K.

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std & skewness & fraction \\
							&   [K]  &   [K] & [K] & rejected [\%]\\
		\hline
noise             		&   0.00 &  0.45 &               0.00 &                - \\
uncorrected       		&  -0.48 &  1.82 &             -14.89 &                - \\
filtered($1\sigma$)  	&  -0.26 &  0.77 &             -16.33 &               72.06 \\
corrected($1\sigma$) 	&   0.43 &  1.70 &             -14.68 &                7.93 \\
corrected($2\sigma$) 	&   0.25 &  1.72 &             -13.86 &                7.93 \\
sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               45.36 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-32 and AWS-41.   }
	\label{tab:correction:stats:32:41}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &  skewness  & fraction\\
						&   [K]  &   [K] & [K]  & rejected [\%]\\
		\hline
	noise       	    	&  -0.00 &  0.45 &               0.00 &               - \\
	uncorrected	    		&  -0.33 &  0.91 &              -3.15 &                - \\
	filtered($1\sigma$)  	&  -0.13 &  0.49 &              -0.40 &               26.18 \\
	corrected($1\sigma$) 	&  -0.05 &  0.59 &              -0.85 &                6.88 \\
	corrected($2\sigma$) 	&  -0.11 &  0.57 &              -1.17 &                6.88 \\
	sreerekha et al   		&  -0.29 &  0.78 &              -2.22 &               45.36 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-33 and AWS-41.   }
	\label{tab:correction:stats:33:41}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction \\
							&   [K]  &   [K] & [K] & rejected [\%]\\
		\hline
 Noise           	  &  -0.00 &  0.63 &               0.00 &                -\\
uncorrected     	  &  -0.27 &  1.06 &              -4.42 &                - \\
filtered($1\sigma$)	  &  -0.13 &  0.68 &              -0.46 &               21.30 \\
corrected($1\sigma$)  &   0.01 &  0.90 &              -1.65 &                2.86 \\
corrected($2\sigma$)  &  -0.09 &  0.83 &              -2.35 &                2.86 \\
sreerekha et al  	  &  -0.13 &  0.70 &              -0.54 &               45.36 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-35 and AWS-43.   }
	\label{tab:correction:stats:35:43}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
							&   [K]  &   [K] & [K] & rejected [\%]\\
		\hline
 Noise            	 &  -0.00 &  0.88 &              -0.01 &               - \\
uncorrected      	 &  -0.16 &  1.02 &              -0.86 &                - \\
filtered($1\sigma$)  &  -0.11 &  0.92 &              -0.13 &                7.38 \\
corrected($1\sigma$) &  -0.07 &  0.93 &              -0.07 &                2.50 \\
corrected($2\sigma$) &  -0.11 &  0.94 &              -0.19 &                2.50 \\
sreerekha et al 	 &  -0.09 &  0.91 &              -0.10 &               45.36 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-36 and AWS-43.   }
	\label{tab:correction:stats:36:43}
\end{table}

@@

[* Finish when Tables 6 and 7 have been checked/corrected. *]

>>>>

We will simply treat cases that matches a correction below a certain value as
``clear-sky''. If the correction limit is denoted as $dtb_{cs}$, the threshold
value, $x_{cs}$, is obtained by inverting the polynomial fit:
\begin{equation}
x_{cs} = f_{cs}^{-1}(dtb_{cs}) 
\label{eq:dtb}
\end{equation}
That is, if $x_m>x_{cs}$ a measurement is classified as clear-sky. If
$x_m\leq x_{cs}$, the measurement is rejected if a pure filtering is made, or
it is adjusted if the correction scheme is applied. We will largely set
$dtb_{cs}$ based on the noise level of the 183\,GHz channel involved, to be
1$\sigma$ or 2$\sigma$ where $\sigma$ refers to the magnitude of measurement
noise (Eq.~\ref{eq:noise}, often called NE$\Delta$T). We will use $1\sigma$ for the development of the scheme, however, the sensitivity of the scheme to 1$\sigma$ and 2$\sigma$  threshold is also provided later in the text.

\subsection{Application of correction scheme}
%
In this section, we test the applicability of the correction scheme in detail.
To analyse the performance of the approach, we apply it to correct the
measurements from C1 using data from C2. Without the availability of actual
data, the simulation dataset but with noise added is used mimic the measurements. The
noise for individual channels is calculated according to
Equation~\ref{eq:noise}. As an example, the results from the channel
combination AWS-34 and AWS-42 are shown. The error in the
predicted measurements is assessed as the deviation to corresponding noise-free
clear-sky value. The average bias, standard deviation and the measure of skewness, of the deviations are also calculated. Skewness gives a measure of asymmetry of the probability distribution of deviations around its mean.

To test the efficacy of the correction scheme, three different models: linear,
quadratic and cubic are evaluated to fit the TB differences between C1 and C2.
For all three models, cases with $Tb2-Tb1 < $ -15\,K are assumed to be ``too
cloudy'' and are not corrected. Also, cases classified as clear according to $1\sigma$ threshold are not corrected. The clear-sky adjustment for all eligible
measurements is calculated from all three
models, and the three predicted datasets are compared.

The occurrence frequency of the deviations from three models is shown in
Fig.~\ref{fig:correction:c34-42:fit} and their corresponding statistics are shown in Table~\ref{tab:correction:stats:34:42:allfits}. The occurrence frequency of the
measurements without any filtering or correction is also plotted as reference
(orange colour). If all measurements are devoid of cloud impact, the
deviations should follow the Gaussian distribution of noise. In such a case, the skewness of the deviations is close to zero.  However, in real conditions, the distribution has a large negative skewness due to the impact of clouds. After correction, all the three models are successful in reducing the cloud impact in the
measurements. The linear model has the lowest reduction in bias (from  -0.75\,K to -0.03\,K) but the highest values for skewness and standard deviation, in comparison to the other two models.  With the linear model, the error distribution of the corrected dataset has a relatively high positive skewness, which is undesirable. The positive skewness can be due to over-correction of cloudy cases, or erroneous correction of clear cases. The cubic  and quadratic models have almost similar statistics for bias and standard deviation, but the skewness in the cubic model is lower. Overall, the cubic model can be said to have the best performance, thus for all the results shown further, a cubic model is used.

In Sec.~\ref{sec:validation} the validation of simulations against ATMS data
(Fig.\ref{fig:pdf:c16-22}) showed that the cloudy cases in the simulations were
underrepresented in comparison to the observations. In order to have a higher
representation of cloudy cases, we thinned the measurement dataset by removing
50\% of the clear-sky cases. Since the distribution of thinned dataset is more closer to real conditions, all the analyses presented further in this section are based on the thinned dataset.

Figure~\ref{fig:correction:c34-42:thinned} shows the deviation of the uncorrected and
corrected measurements to their noise-free clear-sky values for the thinned dataset. The results from
\cite{rekha2012potential} are also shown as reference (see Sec.~\ref{sec:rekha}
for our assumptions). In order to allow a more direct comparison of our
approach with \cite{rekha2012potential}, we also include the
dataset, ``Filtered'', where all cloudy cases are rejected. Apart from the fit
based cloudy classification, it is also assumed that cases with $Tb2-Tb1 < $
-15\,K are ``too-cloudy'' and are rejected.  To analyse the sensitivity of our scheme to noise threhold, as discussed in the previous section, results from two different values of $dtb_{cs}$ are shown. For both values of $dtb_{cs}$ the corresponding clear-sky cut-off
($x_{cs}$) is calculated using Eq~\ref{eq:dtb}. Various metrics corresponding to
the Figure~\ref{fig:correction:c34-42:thinned} are shown in
Table~\ref{tab:correction:stats:34:42:thinned}.

\begin{figure}[!tb]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_AWS-34_AWS-42_allfits}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction, corrected using a linear,
      quadratic and cubic model. The distribution of noise alone is also shown
      as reference. The measurements have been corrected using brightness
      temperatures from AWS-42. The clear/cloudy classification is made with $dtb_{cs} = 1\sigma$ and also cases with $Tb2 - Tb1 > -15$\,K are rejected.}
	\label{fig:correction:c34-42:fit}
\end{figure}
%
\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness  & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		noise                     &   0.00 &  0.63 &               0.00 &                - \\
		uncorrected-all           &  -0.75 &  4.62 &             -11.78 &                - \\
		corrected-linear model    &  -0.03 &  0.75 &               0.48 &                2.84 \\
		corrected-quadratic model &  -0.06 &  0.71 &              -0.34 &                2.84 \\
		corrected-cubic model     &  -0.05 &  0.72 &              -0.23 &                2.84 \\
		\hline
	\end{tabular}
	\caption{Bias, standard deviation (std), and measure of skewness of error distributions
		shown in Figure~\ref{fig:correction:c34-42:fit}.The fraction rejected describes the percentage of cases which are removed. Results from three different fit models are shown: linear, quadratic and cubic.}
	\label{tab:correction:stats:34:42:allfits}
\end{table}
%
\begin{figure}[!tb]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_AWS-34_AWS-42_thinned}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction. The measurements have been
      corrected using a cubic model. The different datasets are: noise
      (simulation dataset), uncorrected (thinned measurements), filtered $1\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 1$\sigma$ are rejected), corrected $1\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 1$\sigma$ are corrected), corrected
      $2\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 2$\sigma$ are corrected), Sreerekha et al (cloudy cases are filtered according to \citet{rekha2012potential}).}
	\label{fig:correction:c34-42:thinned}
\end{figure}
%
\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness  & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	noise             		&   0.00 &  0.63 &              -0.01 &                - \\
	uncorrected     		&  -1.27 &  6.05 &              -8.97 &                - \\
	filtered($1\sigma$)  	&  -0.13 &  0.68 &              -0.25 &               17.54 \\
	corrected($1\sigma$) 	&  -0.06 &  0.76 &              -0.46 &                4.99 \\
	corrected($2\sigma$) 	&  -0.11 &  0.75 &              -0.69 &                4.99 \\
	sreerekha et al   		&  -0.20 &  0.78 &              -1.00 &               45.36 \\			
		\hline
\end{tabular}
\caption{Bias, standard deviation (std), and measure of skewness of the
	error distributions of datasets shown in Figure~\ref{fig:correction:c34-42:thinned}.}
\label{tab:correction:stats:34:42:thinned}
\end{table}

The distributions of filtered data are non-Gaussian. The right side of the
distribution follows measurement noise while the left side is skewed. The
skewness in the distribution is due to cloud impacts which pass through the
clear-sky threshold. The higher skewness in ``Sreerekha et al'' is mainly
beacuse their method only aims at removing cloud impacts above 4\,K.
Their approach also leads to a high rejection fraction (45.36\%). The filtering
method introduced here leads to a considerable lower rejection of data
(17.54\%).

If the correction part for $1\sigma$ is added, the rejection is decreased even further (4.99\%)
and the bias is also improved (from -1.27 to -0.06\,K). On the other hand, the
correction gives some increase in standard deviation and skewness, compared to
filtering alone. A correction using $2\sigma$ gives poorer performance, in particular the reduction in bias is smaller and the skewness is increased.

%
\subsection{Application of correction scheme using AWS-4X}
%
\begin{figure}[!t]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_AWS-32_AWS-4X_thinned}
	\caption{Same as Fig.~\ref{fig:correction:c34-42:thinned}, but for channel combinations AWS-32 and AWS-4X. The dataset ``corrected 2$\sigma$'' is not shown.  }
	\label{fig:correction:c32-4X:thinned}
\end{figure}
%

@@

Fig.~\ref{fig:correction:c32-4X:thinned} shows the deviations of the
measurements to clear-sky values before and after correction, and the
corresponding metrics are provided in Table~\ref{tab:correction:stats:32:4X}.
With clear/cloudy classification for $dtb_{cs} = 1\sigma$, around 85\% of the
total measurements are classified as cloudy and are rejected in pure-filtering.
Rejecting all the cloudy cases reduces the average bias in the measurements
from -2.25\,K to -0.21\,K, while with the approach from
\citet{rekha2012potential} only 45.36\% of the data is rejected and the average
bias reduces to -0.41\,K. When all the cloudy cases, except the ``too cloudy'',
are corrected, the total bias increases to 0.88\,K. The unusually high fraction
of cloudy cases and an increase in bias on correction suggests misclassification
of clear cases as cloudy. Since, the weighting functions of AWS-32 and AWS-4X
are poorly matched, their relationship is inadequate to estimate the cloud
impact in AWS-32. Without any additional information, the regression approach
can only provide a successful filtering in comparison to the original approach
described by \citet{rekha2012potential}, although at the cost of high rejection
fraction. Additional information e.g., TB from other channels, is necessary
improve the accuracy of the correction.

\begin{table}[!h]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std & skewness & fraction \\
						&   [K]  &   [K] & [-] 		& rejected [\%]\\
		\hline
Noise             		&  0.00 &  0.45 &               0.01 &                - \\
uncorrected       		&  -2.25 &  8.94 &              -6.85 &                - \\
filtered($1\sigma$)  	&  -0.21 &  0.51 &              -0.65 &               85.43 \\
corrected($1\sigma$) 	&   0.88 &  1.76 &              -1.30 &                5.35 \\
corrected($2\sigma$) 	&   0.76 &  1.80 &              -1.07 &                5.35 \\
sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               45.36 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combinations: AWS-32 and AWS-4X.  }
	\label{tab:correction:stats:32:4X}
\end{table}

@@

Table~\ref{tab:correction:stats:32:41} shows the statistics when AWS-32 is
corrected using AWS-41. The statistics of the filtered dataset are better than
the approach by \cite{rekha2012potential}, while the corrected data have poorer
statistics. This is not surprising as the weighting function match between
AWS-32 and AWS-41 is poor. The correction using $2\sigma$ as threshold works
better $1\sigma$. This is an exception, the reverse is valid for AWS-34/42 (as
mentioned) and the channel combinations discussed below.

Table~\ref{tab:correction:stats:33:41} shows the statistics when AWS-33 is
corrected using AWS-41. The TB differences for this combination and the cloud
impact in AWS-33 are highly correlated. Rejecting the cloudy cases reduces the
average bias in the measurements from -1.74\,K to -0.13\,K, while a correction
of cloudy cases reduces the bias further to 0.05\,K. The standard deviation and skewness of the corrected dataset are higher than pure-filtering, but smaller than the approach by  ``sreerekha et al''. Using $2\sigma$ threshold corrects a smaller fraction of cases than $1\sigma$ but the overall statistics are poorer in comparison to $1\sigma$, but still better than the ``sreerekha et al''.

Table~\ref{tab:correction:stats:35:43} shows the statistics for the combination AWS-35 and AWS-43. Here the two filtered datasets have a comparable performance, while on correction, the bias is reduced, but skewness and standard deviation are increased. After correction ($1\sigma$) the bias due to cloudy measurements reduces from -0.83\,K to 0.01\,K while rejecting only 2.86\% of the total cases.  The performance of $1\sigma$ threshold in this case is also better than $2\sigma$.

Table~\ref{tab:correction:stats:36:43} shows the statistics when AWS-36 is
corrected using AWS-43. For this combination, the weighting functions have a
poor match, but the TB differences and the cloud impact are strongly
correlated, as the cloud impact in AWS-36 is relatively low in comparison to
other 183\,GHz channels. The low fraction of rejection (7.38\%) also shows that
most of the measurements are without cloud impact. However, the small fraction
of cloudy cases which are corrected, helps in successfully reducing the average
bias from -0.54\,K to -0.07\,K.

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std & skewness & fraction \\
							&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
noise             		&   0.00 &  0.45 &               0.00 &                - \\
uncorrected       		&  -2.25 &  8.94 &              -6.85 &                 - \\
filtered($1\sigma$)  	&  -0.26 &  0.77 &             -16.33 &               72.06 \\
corrected($1\sigma$) 	&   0.43 &  1.70 &             -14.68 &                7.93 \\
corrected($2\sigma$) 	&   0.25 &  1.72 &             -13.86 &                7.93 \\
sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               45.36 \\
\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-32 and AWS-41.   }
	\label{tab:correction:stats:32:41}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &  skewness  & fraction\\
						&   [K]  &   [K] & [-]  & rejected [\%]\\
		\hline
	noise       	    	&  0.00 &  0.45 &               0.00 &               - \\
	uncorrected	    		&  -1.74 &  7.45 &              -7.77 &                - \\
	filtered($1\sigma$)  	&  -0.13 &  0.49 &              -0.40 &               26.18 \\
	corrected($1\sigma$) 	&  -0.05 &  0.59 &              -0.85 &                6.88 \\
	corrected($2\sigma$) 	&  -0.11 &  0.57 &              -1.17 &                6.88 \\
	sreerekha et al   		&  -0.29 &  0.78 &              -2.22 &               45.36 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-33 and AWS-41.   }
	\label{tab:correction:stats:33:41}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction \\
							&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
 Noise           	  &  0.00 &  0.63 &               0.00 &                -\\
uncorrected     	  &  -0.83 &  4.50 &             -10.85 &                - \\
filtered($1\sigma$)	  &  -0.13 &  0.68 &              -0.46 &               21.30 \\
corrected($1\sigma$)  &   0.01 &  0.90 &              -1.65 &                2.86 \\
corrected($2\sigma$)  &  -0.09 &  0.83 &              -2.35 &                2.86 \\
sreerekha et al  	  &  -0.13 &  0.70 &              -0.54 &               45.36 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-35 and AWS-43.}
	\label{tab:correction:stats:35:43}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
							&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
 Noise            	 &  0.00 &  0.88 &              -0.01 &               - \\
uncorrected      	 &  -0.54 &  3.40 &             -12.26 &                - \\
filtered($1\sigma$)  &  -0.11 &  0.92 &              -0.13 &                7.38 \\
corrected($1\sigma$) &  -0.07 &  0.93 &              -0.07 &                2.50 \\
corrected($2\sigma$) &  -0.11 &  0.94 &              -0.19 &                2.50 \\
sreerekha et al 	 &  -0.09 &  0.91 &              -0.10 &               45.36 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-36 and AWS-43.   }
	\label{tab:correction:stats:36:43}
\end{table}

@@

For AWS-32, filtering based either AWS-4X or AWS-41 has a very high rejection rate, though the resulting dataset has low error. The high fraction of rejection can increase the probability of removing ``true'' clear cases. After correction, the error distributions are asymmetric and have large bias and standard deviation. Among the two combinations, the dataset corrected with AWS-41 has slightly better bias and standard deviation. As an exception to other 183\,GHz channels, the correction scheme for AWS-32 works better for $2\sigma$ threshold, as with a larger value of noise, relatively smaller number of cases are corrected. The effect of mismatch between weighting functions for AWS-32 and AWS-4X/41 is reflected in the performance of our correction scheme.
